Looking Back: One Year HPC Certification Forum

### 2019-04-11 paper.tex
Skill tree update

This article describes the current status of the certification program by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
Our previous work described the evolution from the project that sparked the initial activity that lead to the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.

@@

@@

\begin{figure*}[tb!]
	\centering
	\includegraphics[width=15.0cm]{skill-tree_top_levels.jpg}
  \vspace*{-2em}
	\caption{Top Level Competences}
	\label{f_top_level_competences}
\end{figure*}

@@

\section{Certification Program}

The certification program serves two purposes:
1) the definition and organization of fine-grained competences (skills);
2) the establishment of certificates and (online) exams that confirm that users possess a certain skill.
Note that the certification program does not regulate the content -- the definition of skills and certificates is separated from content creation.
This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
Teaching material should be marked to indicated which skills it covers.
In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
We assume that the collaboration of scientific institutions will complement each other in producing a rich variety of content for the different learning styles.

@@

\section{Conclusions}

The HPC Certification program offers a strategy to classify and organize HPC competences.
While the idea started with the PeCoH project, we are supporting the HPC Certification Forum\footnote{\url{https://hpc-certification.org}} which is an independent international body that aims to sustain the work.
The certification forum has the role of a (virtual) central authority to curate and maintain the skill tree and certificates.
Moreover, the forum supports tools and an ecosystem around the competences.

>>>>

This article describes the current status of the certification program offered by the HPC Certification Forum by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
Our previous work described the evolution from the project that sparked the initial activity that lead to the independent body of the HPC Certification Forum \cite{TAHCPKHHSS19}.

@@

The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain a skill tree of competences, the creation of certificates, and examination of practitioners to attest certificates.
Moreover, the forum supports tools and an ecosystem around the competences.

\jk{Integrate}

1) the definition and organization of fine-grained competences (skills);
2) the establishment of certificates and (online) exams that confirm that users possess a certain skill.
Note that the certification program does not regulate the content -- the definition of skills and certificates is separated from content creation.
This allows the re-use of existing content but also allows to create a new ecosystem in which HPC centers or commercial companies could offer the best teaching material.
Teaching material should be marked to indicated which skills it covers.
In the future, the program may provide means to register and reference existing content of third-parties allowing users to browse the skills and navigate to teaching material.
We assume that the collaboration of scientific institutions will complement each other in producing a rich variety of content for the different learning styles.

@@

@@

\begin{figure*}[tb!]
	\centering
	\includegraphics[width=15.0cm]{skill-tree}
	\caption{Top Level Competences with an expansion of PE4}
	\label{f_top_level_competences}
\end{figure*}

\jk{Old stuff}

@@
